---
title: "zhcweek5"
author: "Zhuoyang Chen"
date: "February 7, 2020"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{zhcweek5}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##This package is a practice of ANGDS Week5 assignment  
There is only one function **reading_in** in this package.

### Reading in  
Function for parsing the text output of FastQC. It extracts the values for a specific test run by FastQC on asingle fastq file.
####usage  
reading_in(file=<fastq_data.txt>, sample = <phenotype/accession#>, test = <test_type>)

####arguments  
#####Input:  
file: string that specifies the path to an individual FastQC result file (tyically named "fastqc_data.txt)
sample: A sample name that would be specified by user
test: Indicate which test results should be extracted. Default: "Per base sequence quality". Other options are, for example, "Pertile sequence quality", "Per sequence quality score" etc.

#####output:  
dat: data.frame with the values of a single FastQC test result.

####examples  
res <- reading_in(file =
"acinar-3_S9_L001_R1_001_fastqc/fastqc_data.txt")

#### Code Explanation
**syscommand** is to generate the command that used by your computer system to pre-process the data file you provide.

#####paste0
Paste string without any sapce.

#####sed
The first section before '|' is to select a range of lines according to given patterns. In the code, it select lines from the line that contains "Per base sequence quality" to the line that first meets "END_MODULE". Then the section after '|' is to remove lines that start with symbol ">>", which are actually the first and the last line.

###ggplot2 on data df
```{r ggplot}
getwd()
#install.packages("../zhcweek5.tar.gz")
#use zhcweek5::df
library(zhcweek5)
library(ggplot2)
dat <- fastq_df
WT <- rep("WT",51)
SNF2 <- rep("SNF2",51)
type <- c(WT,WT,SNF2,SNF2)
dat$type <- type
p <- ggplot(dat, aes(x = `#Base`, y = Mean)) + geom_point(aes(color = sample))
library(patchwork)
p1 <- p + facet_grid(. ~ type) + ylim(0,41)
```

```{r, fig.width=7,fig.height=4}
print(p1)
```

